ms_russia_results

### 2024-04-19 ms-russia-results.Rmd
update stats text

colnames(top_intermediates) <- c("Intermediate Exporter", "Consumption (live weight tonnes)", "Percent (%)")
```
### Top Intermediate Exporters for Russian sourced products to the US (2015-2019)
`r reactable(top_intermediates)`

@@

```{r unfriendly_countries_consumption}
unfriendly_rus_consumption <- consumption %>%
  filter(sanctions_towards_russia == "Russia unfriendly countries" &
           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

@@

```{r friendly_countries_consumption}
friendly_rus_consumption <- consumption %>%
  filter(sanctions_towards_russia == "Russia friendly countries" &
           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

@@

friendly_consumption_percent_change = 100 * ((friendly_consumption_post - friendly_consumption_pre) / friendly_consumption_pre)
```

Countries which did not impose sanctions (“friendly countries”) also increased consumption of Russian products (`r signif(friendly_consumption_percent_change, digits = 3)`% in 2015–2016 compared to 2013–2014).

>>>>

colnames(top_intermediates) <- c("Intermediate Exporter", "Consumption (live weight tonnes)", "Percent (%)")
```

### Top Intermediate Exporters for Russian sourced products to the US (2015-2019)
`r reactable(top_intermediates)`

@@

```{r unfriendly_countries_consumption}
unfriendly_rus_consumption <- consumption %>%
  filter(consumer_iso3c != "RUS" &
           sanctions_towards_russia == "Russia unfriendly countries" &
           ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

@@

```{r friendly_countries_consumption}
# Look at 2014 drop in consumption of Russian products by friendly countries
friendly_rus_consumption <- consumption %>%
  filter(consumer_iso3c != "RUS" & 
           sanctions_towards_russia == "Russia friendly countries" &
           ((year %in% 2012:2013) | (year %in% 2014))) %>%
  mutate(period = case_when(
    year %in% 2012:2013 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(sanctions_towards_russia, period) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)/length(unique(year))) %>%
  ungroup()

@@

friendly_consumption_percent_change = 100 * ((friendly_consumption_post - friendly_consumption_pre) / friendly_consumption_pre)

# Friendly country consumption of Russian products following 2014
friendly_consumption_2020 <- consumption %>%
  filter(consumer_iso3c != "RUS" & 
           sanctions_towards_russia == "Russia friendly countries" &
           year == 2020) %>%
  group_by(year) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  pull(consumption_live_t)

friendly_consumption_percent_change_2020 = 100 * ((friendly_consumption_2020 - friendly_consumption_pre) / friendly_consumption_pre)
```

Countries which did not impose sanctions (“friendly countries”) decreased consumption of Russian products (`r signif(friendly_consumption_percent_change, digits = 3)`% in 2014 compared to 2012–2013), but their consumption quickly rebounded, exceeding `r floor(friendly_consumption_percent_change_2020)`% of the pre-2014 value in 2020.
